Multisensor Architecture for an Intersection Management System

### 2019-01-27 ch4-results.tex
Added TODOs
Format improved in section 3.1 and 3.2.

In this chapter is presented the experimental setup used to deploy and test the proposed architecture. First is described the data and hardware and software specifications. Then, two implemented configurations of the system are presented. Finally, results are summarized and analysed.

\section{Experimental Setup}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{fig/4/intersection-config2.pdf}
\caption{Possi dataset configuration}
\label{possi_img}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.2]{fig/4/sensors_overview.jpeg}
\caption{Overview of sensors data. Left: Laser scanners, Right: Camera.}
\label{possi_sensors}
\end{figure}

%\subsection{Data}
The selected dataset for testing the system is the one from POSSi project (section \ref{possi_ds}). It contains 6 laser-scanners raw readings and a video from a camera located over the intersection. Figure \ref{possi_img} depicts the configuration used by this dataset. In figure \ref{possi_sensors} is shown the data from each type of sensors, laser scanners and camera. The ground truth data used for validation is the vehicle count over 3 of the 5 legs of the intersection, taking into account the time at which a vehicle appears. This groundtruth data was generated manually.

@@

\section{Test Configurations}

@@

The following table lists all used blocks and assigns an ID for each one. Those IDs are used in the graph description in its own section. Also, bold nodes and connections indicate multiple instance of the same element. The figure \ref{tconf1} shows the  configuration used for processing just video data. Figure \ref{tconf2} shows the configuration when a set of lasers is added to the single-camera configuration. The blue line represents the fusion at node K, which is fusion on virtual sensors level. The purple line represents the fusion at flow rate level.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.6]{fig/4/test_configuration1.pdf}
\caption{Single camera configuration}
\label{tconf1}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.6]{fig/4/test_configuration2.pdf}
\caption{Multiple lasers and camera configuration}
\label{tconf2}
\end{figure}

@@

@@

>>>>

In this chapter is presented the experimental setup used to deploy and test the proposed architecture. First is described the data and hardware and software specifications. Then, two implemented configurations of the system are presented. Finally, results are summarized and analysed, comparing both configurations and different fusion approaches.

\section{Experimental Setup}
%\todo{First paragraph then figure}

%\subsection{Data}
The selected dataset for testing the system is the one from POSSi project (section \ref{possi_ds}). It contains 6 laser-scanners raw readings and a video from a camera located over the intersection. Figure \ref{possi_img} depicts the configuration used by this dataset and the data from each type of sensors, laser scanners and camera. The ground truth data used for validation is the vehicle count over 3 of the 5 legs of the intersection, taking into account the time at which a vehicle appears. This groundtruth data was generated manually.

\begin{figure}[ht!]
\begin{subfigure}{\textwidth}
\centering
\includegraphics[scale=0.8]{fig/4/intersection-config2.pdf}
\caption{Global configuration}
\label{possi_img}
\end{subfigure}

\begin{subfigure}{\textwidth}
\centering
\includegraphics[scale=0.2]{fig/4/sensors_overview.jpeg}
\caption{Overview of sensors data. Left: Laser scanners, Right: Camera.}
\end{subfigure}
\caption{Possi dataset configuration.}
\label{possi_sensors:a}
\end{figure}

@@

\section{Test Configurations}
%\todo{First paragraph then figure}

@@

The table \ref{desc_test_config} lists all used blocks and assigns an ID for each one. Those IDs are used in the graph description in its own section. Also, bold nodes and connections indicate multiple instance of the same element. The figure \ref{tconf2} shows the  configuration used for processing just video data the configuration when a set of lasers is added to the previous configuration. The blue line represents the fusion at node K, which is fusion on virtual sensors level. The purple line represents the fusion at flow rate level.

\todo{Explain evaluation params}

\begin{figure}[ht!]
%\centering

\begin{subfigure}{\textwidth}

\includegraphics[scale=0.6]{fig/4/test_configuration1.pdf}
\caption{Single camera configuration.}
%\label{tconf1}
%\end{figure}
\end{subfigure}

%\begin{figure}[ht!]
%\centering

\begin{subfigure}{\textwidth}
\includegraphics[scale=0.6]{fig/4/test_configuration2.pdf}
\caption{Multiple lasers and camera configuration.}

\end{subfigure}
\caption{Test configurations.}
\label{tconf2}
\end{figure}

@@

\begin{figure}[htb!]
\centering
\includegraphics[scale=0.4]{fig/4/conf_mat.jpeg}
\caption{Results for the multisensor implementation using four different fusion approaches}
\label{vl_res}
\end{figure}

@@

\todo{Sumarise and discuss results}
